Binary companions of red giant stars in \apogee\ \DR: \\ Search method and catalog of $>$4,500 systems

### 2018-03-08 paper/1-catalog/twoface-catalog.tex
title and change control to comparison

\title{Binary companions of red giant stars in \apogee\ \DR}

@@

\subsection{Null control sample}
\label{sec:control-sample}

We construct a control sample of simulated data with no RV variability to assess
our false-positive rates in the selections below (see
\sectionname~\ref{sec:catalogs}).
We randomly pick \ncontrol\ stars from the parent sample used in this work and
replace the visit velocity measurements with simulated data.
For each star $n$, we randomly sample an excess variance parameter value from
the prior, $s_n$.
For each visit $k$, we then sample a new velocity $v_{nk}$ by drawing from a
Gaussian with mean equal to the mean of the real data visit velocities,
$\bar{v}_n$, and variance equal to the sum of the visit variance (uncertainty),
$\sigma_{nk}$, and the excess variance,
\begin{equation}
    v_{nk} \sim \mathcal{N}(\bar{v}_n, \sigma_{nk}^2 + s_n^2) \quad .
\end{equation}
When we save the control data, we only store the visit uncertainty and
``forget'' the fact that the simulated data is generated with excess variance.

@@

We also run on the null control sample (see
\sectionname~\ref{sec:control-sample}) with the same parameters.
From the control sample run, 13 ``stars'' are flagged as \emph{needs MCMC}, and
1023 are flagged as ``needs more prior samples'';
For these control sample stars, we don't continue sampling with \thejoker\ or
MCMC and only use the ($<$\nposterior) posterior samples returned from the
\thejoker.
% See: Sample K cuts.ipynb

@@

We select a sample of stars that confidently have companions using percentiles
computed from the log of the posterior samples in the velocity semi-amplitude
parameter, $\ln K$.
\figurename~\ref{fig:lnK-percentiles}, shows the distribution of 1st percentiles
of $\ln K$ computed for all stars with posterior samplings from \thejoker\
(filled, blue histogram), along with the same for posterior samplings for the
null control sample (solid, dark line).
To select stars with companions, we use a cut in the 1st percentile of the $\ln
K$ samples such that $<1\%$ of the control sample is selected, i.e. our
estimated false positive rate is $<1\%$.
We use a threshold of $\ln K = 0$ to meet this constraint (vertical, dashed line
in \figurename~\ref{fig:lnK-percentiles}); \nhighK\ stars pass this cut.
For brevity below, we refer to this sample as the ``high-$K$'' stars, and the
complimentary sample as the ``low-$K$'' stars.

% Notebook: "Sample K cuts.ipynb"
\begin{figure}[h]
\begin{center}
\includegraphics[width=0.8\textwidth]{lnK-percentiles}
\end{center}
\caption{%
Distribution of 1st percentiles in $\ln K$ (in units of \kms) for the parent
\apogee\ sample (blue, filled) and for the control sample (solid, dark line).
The vertical line (dashed, orange) indicates our adopted cut to select high-$K$
stars that likely have companions; $<1\%$ of the control sample falls above this
cut.
\label{fig:lnK-percentiles}
}
\end{figure}

@@

>>>>

\title{Binary companions of red giant stars in \apogee\ \DR: \\
       Search method and catalog of $>$4,500 systems}

@@

\subsection{Null comparison sample}
\label{sec:control-sample}

We construct a comparison sample of simulated data with no RV variability to
assess our false-positive rates in the selections below (see
\sectionname~\ref{sec:catalogs}).
We randomly pick \ncontrol\ stars from the parent sample used in this work and
replace the visit velocity measurements with simulated data.
For each star $n$, we randomly sample an excess variance parameter value from
the prior, $s_n$.
For each visit $k$, we then sample a new velocity $v_{nk}$ by drawing from a
Gaussian with mean equal to the mean of the real data visit velocities,
$\bar{v}_n$, and variance equal to the sum of the visit variance (uncertainty),
$\sigma_{nk}$, and the excess variance,
\begin{equation}
    v_{nk} \sim \mathcal{N}(\bar{v}_n, \sigma_{nk}^2 + s_n^2) \quad .
\end{equation}
When we save the comparison data, we only store the visit uncertainty and
``forget'' the fact that the simulated data is generated with excess variance.

@@

We also run on the null comparison sample (see
\sectionname~\ref{sec:control-sample}) with the same parameters.
From the comparison sample run, 13 ``stars'' are flagged as \emph{needs MCMC},
and 1023 are flagged as ``needs more prior samples'';
For these comparison sample stars, we don't continue sampling with \thejoker\ or
MCMC and only use the ($<$\nposterior) posterior samples returned from the
\thejoker.
% See: Sample K cuts.ipynb

@@

We select a sample of stars that confidently have companions using percentiles
computed from the log of the posterior samples in the velocity semi-amplitude
parameter, $\ln K$.
\figurename~\ref{fig:lnK-percentiles}, shows the distribution of 1st percentiles
of $\ln K$ computed for all stars with posterior samplings from \thejoker\
(filled, blue histogram), along with the same for posterior samplings for the
null comparison sample (solid, dark line).
To select stars with companions, we use a cut in the 1st percentile of the $\ln
K$ samples such that $<1\%$ of the comparison sample is selected, i.e. our
estimated false positive rate is $<1\%$.
We use a threshold of $\ln K = 0$ to meet this constraint (vertical, dashed line
in \figurename~\ref{fig:lnK-percentiles}); \nhighK\ stars pass this cut.
For brevity below, we refer to this sample as the ``high-$K$'' stars, and the
complimentary sample as the ``low-$K$'' stars.

% Notebook: "Sample K cuts.ipynb"
\begin{figure}[h]
\begin{center}
\includegraphics[width=0.8\textwidth]{lnK-percentiles}
\end{center}
\caption{%
Distribution of 1st percentiles in $\ln K$ (in units of \kms) for the parent
\apogee\ sample (blue, filled) and for the comparison sample (solid, dark line).
The vertical line (dashed, orange) indicates our adopted cut to select high-$K$
stars that likely have companions; $<1\%$ of the comparison sample falls above
this cut.
\label{fig:lnK-percentiles}
}
\end{figure}

@@

% TODO:
% Notebook: "Results"
% \begin{figure}[h]
% \begin{center}
% \includegraphics[width=\textwidth]{infer-jitter}
% \end{center}
% \caption{%
% Inferred prior over excess variance parameter ($y = \ln s^2$) using posterior
% samples for 1,825 lower-RGB stars with $>10$ visits.
% Left and right panels show the distribution corresponding to the
% maximum-likelihood parameters $(\mu_y, \sigma_y) = (9.50, 1.64)$ in log and
% linear, respectively.
% \label{fig:infer-jitter}
% }
% \end{figure}
